Replicate earlier study

### 2023-04-04 paper.qmd
slowly getting going

abstract: |
  This document is a sample illustrating the Quarto `ieeetran` template.
  It includes the key elements of a scientific articles 
  (references, equations, figures, tables, code, cross references).
  The template enables the generation of IEEE-formatted article from a Jupypter notebook.
keywords: [template, demo]
reference-section-title: References
bibliography: bibliography.bib
note: Extra footnote.

@@

# Data and Conceptual Approach

@@

$$spacing deviation (t) = ref{\_}time(trailer_{(t)}) - ref{\_}time(leader_{(t - s)})$$

>>>>

abstract: |
  In light of the on-going discussion on climate change, operational efficiency of air navigation has gained a higher visibility.
  Efficient operations will positively influence the fuel burn by airspace users. 
  While the development and introduction of novel aircraft airframe and propulsion technologies, 
  the global pickup rate of sustainable aviation fuel, and benefits mechanism of market-based measures promise a positive effect
  over time, >> reducing unnecessary contraints on airspace users can be immediately deployed. 
  There is still a considerable benefit pool for arrival operations. 
  This proof-of-concept paper explores the use of open data for the analysis of operational efficiency within the extended terminal airspace.
  To characterise the potentail benefit pool, a method to quantify the spacing deviation between successive flights is developed.
  This paper summarises the conceptual approach and reports on the first findings of an use-case analysis for a subset of European airports.
  The results show the general feasibility of the approach and help to identify requirements for the further development of operational performance measures. 
keywords: [template, demo]
reference-section-title: References
bibliography: bibliography.bib
note: Extra footnote.

@@

# Conceptual Approach and Data

## Research Approach

This paper follows an exploratory research process (c.f. @fig-research-approach).
We frame the work as a operational performance analytical problem.

```{r}
#| label: fig-research-approach
#| fig-cap: Exploratory research approach
#| out-width: 45%     # 2 column half-size
knitr::include_graphics("./figures/exploratory-research-concept.png")
```

@@

$$\begin{aligned}
spacing \text{ } deviation (t) =  ref{\_}time(trailer_{(t)}) - \\ref{\_}time(leader_{(t - s)})
\end{aligned}$${#eq-spacing-deviation}

```{r}
#| label: fig-follower-leader-example
#| fig-cap: Example timeline of spacing deviations between interacting arrivals
#| out-width: 45%     # 2 column half-size
knitr::include_graphics("./figures/example-follower-leader-pairs.png")
```

@eq-spacing-deviation does something.

### 2023-04-04 x_replicate.qmd
slowly getting going

do for 1 pair
```{r}
rq <- my_pairwise_spacing("400550-0", "89505a-0",.t_trail = 134, .bins = tessel_lookup)

@@

ggplot() + 
  geom_line(data = rq,  aes(x = STEP, y = MIN_TIME_OFF), alpha = 0.5) +
  geom_line(data = rqq, aes(x = STEP, y = SPACING), color = "blue")
```

>>>>

do for 1 pair
```{r}
rq <- my_pairwise_spacing("400550-0", "89505a-0",.t_trail = 134, .bins = tessel_lookup) 
rq1 <- my_pairwise_spacing("89505a-0","40054d-0", .t_trail = 122, .bins = tessel_lookup)
rq2<- my_pairwise_spacing("71005e-0", "4007f2-0", .t_trail = 91, .bins = tessel_lookup)
rq3 <- my_pairwise_spacing("4007f2-0","896464-0", .t_trail = 98, .bins = tessel_lookup)

rq <- rq |> bind_rows(rq1, rq2, rq3) |> 
  mutate(GID = paste(UID, SEQ_UID, RWY, sep = "-"))

@@

rqq <- rqq |> filter(!grepl(pattern = "-NA-", x = GID), STEP < 1250)

ggplot() + 
 # geom_line(data = rq,  aes(x = STEP, y = MIN_TIME_OFF, group = GID), alpha = 0.5) +
  geom_line(data = rqq, aes(x = STEP, y = SPACING, group = GID, color = GID) ) +  #  = "blue")
  labs(x = "time to fly [sec]", y = "spacing deviation [sec]"
       ,color = "follower-leader-pair") +
  theme(legend.position = c(0.2,0.2))
```
